Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-07-05 ms.tex
added final sentence to correlation slope discussion

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the basic conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. However, it is also
apparent that the improvement in $\chi^2_{\nu}$ for single-MBB versus double
MBB models found here is substantially less dramatic 
($\Delta\chi^2_{\nu}$=4.32) than that found in FDS99 
($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the exquisite 
narrow-band frequency coverage of FIRAS, especially near the dust SED peak, 
which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model.

% acknowledge that the preference for two MBBs is relatively weak when swapping
% in Planck for FIRAS, probably due to the

@@

\subsection{Global Parameters Revisited}
% discuss goodness of fit tests based on running Markov chains with different
% sets of global parameters

>>>>

Lastly, we calculate the optimal single-MBB fit to the \PLANCK+DIRBE 
correlation slope spectrum. The best-fit single MBB has $\beta$=1.59, 
$T$=19.63, and $\chi^2_{\nu}$=5.65, indicating a significantly worse fit to the
data than our best-fit two-component model (model 2). Thus, our \PLANCK+DIRBE 
correlation slope analysis has confirmed the main conclusion of FDS99 and 
others e.g. \cite{reach95}, that the FIR/submm dust SED prefers two MBBs to 
just one, but, for the first time, independent of FIRAS. Still, it is apparent 
that the improvement in $\chi^2_{\nu}$ for single-MBB versus double MBB models 
found here is substantially less dramatic ($\Delta\chi^2_{\nu}$=4.32) than that
found in FDS99 ($\Delta\chi^2_{\nu}$=29.2). This is likely attributable to the 
exquisite narrow-band frequency coverage of FIRAS, especially near the dust SED
peak, which makes FIRAS a better suited data set than \PLANCK~for a detailed 
analysis of the globally best-fit dust SED model. In $\S$\ref{sec:hier}, we
confirm the basic conclusions of this section via an MCMC-based approach in
which the dust temperature is allowed to vary spatially.

@@

\subsection{Global Parameters Revisited}
\label{sec:hier}
% discuss goodness of fit tests based on running Markov chains with different
% sets of global parameters
